Ktirio Urban Building: A Computational Framework for City Energy Simulations Enhanced by CI/CD Innovations on EuroHPC Systems

### 2024-11-01 article.hid2-ub-cicd.ppam24.tex
add  information of required supercomputing environments #16

Building on the foundations of the Feel++ framework, this paper introduces an innovative CI/CD environment specifically designed for deployment on EuroHPC JU supercomputers. This environment enhances our ability to develop and test simulations rapidly and provides a robust platform for deploying and running these simulations at multiple scales. Integrating EuroHPC JU infrastructures represents a significant advancement in making high-performance computing resources accessible for urban simulation studies.

@@

The Urban Building pilot utilizes the Feel++ framework, supported by a robust CI/CD framework that facilitates efficient development and deployment. %This section outlines how GitHub Actions and Docker streamline the entire process, ensuring the robustness and productivity of the software development lifecycle.

@@

\begin{wrapfigure}{R}{.7\linewidth}
    \centering
    \includegraphics[width=\linewidth,page=1]{img-ub-devops-hpcops.pdf}
    \caption{KUB standard DevOps}
    \label{fig:kub-devops}
\end{wrapfigure}
This framework leverages cutting-edge computational technologies, ensuring the high performance and accuracy of the Feel++ framework and Feel++-based applications.
It sets a benchmark for integrating modern software frameworks with advanced HPC infrastructure to significantly advance computational research and applications.

\Cref{fig:kub-devops} shows that the CI/CD standard DevOps framework for KUB uses similar steps.

\Cref{fig:kub-hpcops} finally shows the HPCOps deployed on EuroHPC systems to check the parallel properties and correctness of the pilot on large-scale cases. It extends Feel++ HPC ops with additional steps to handle our complex pre- and post-processing steps.

>>>>

Building on the foundations of the Feel++ framework, this paper introduces an innovative CI/CD environment specifically designed for deployment on EuroHPC JU supercomputers. 
This environment enhances our ability to develop and test simulations rapidly and provides a robust platform for deploying and running these simulations at multiple scales. 
By leveraging containerized environments, we ensure that all dependencies are encapsulated, making the simulations portable and reproducible across different supercomputing resources. 
These containers are deployed on EuroHPC JU infrastructures, which represents a significant advancement in making high-performance computing resources accessible for urban simulation studies. 
The use of containers also simplifies software management and ensures consistency in the deployment process, enabling seamless scalability and reliability across EuroHPC systems.

@@

The Urban Building pilot utilizes the Feel++ framework, supported by a robust CI/CD framework that facilitates efficient development and deployment.
A critical component for both Feel++ and KUB is the use of containerized environments, which encapsulate all necessary dependencies and configurations.

%This section outlines how GitHub Actions and Docker streamline the entire process, ensuring the robustness and productivity of the software development lifecycle.

@@

\begin{wrapfigure}{R}{.7\linewidth}
    \centering
    \includegraphics[width=\linewidth,page=1]{img-ub-devops-hpcops.pdf}
    \caption{KUB standard DevOps}
    \label{fig:kub-devops}
\end{wrapfigure}
This framework leverages cutting-edge computational technologies, ensuring the high performance and accuracy of the Feel++ framework and Feel++-based applications.
It sets a benchmark for integrating modern software frameworks with advanced HPC infrastructure to significantly advance computational research and applications.
\Cref{fig:kub-devops} shows that the CI/CD standard DevOps framework for KUB uses similar steps.
\Cref{fig:kub-hpcops} finally shows the HPCOps deployed on EuroHPC systems to check the parallel properties and correctness of the pilot on large-scale cases. It extends Feel++ HPC ops with additional steps to handle our complex pre- and post-processing steps.
